---
title: "Assigment - kNN DIY"
author:
  - Thanh Hung Lê - Author
  - Qiwen Chen - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---


```{r}
library(readr)
library(tidyverse)
library(forcats)
library(class)
library(caret)
library(e1071)
```

---

## Business Understanding
text and code here

## Data Understanding
text and code here
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-hcvdat0.csv"
rawDF <- read_csv(url)
View(rawDF)
str(rawDF)
```


## Data Preparation
text and code here
```{r}
cleanDF <- rawDF[,-1]
head(cleanDF)

cntDiag <- table(cleanDF$Category)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
propDiag

cleanDF$Category <- fct_collapse(cleanDF$Category, donor = c("0=Blood Donor", "0s=suspect Blood Donor"), 
                                 hepatitis = c("1=Hepatitis", "2=Fibrosis", "3=Cirrhosis")) #I eliminate the category "suspectdonor" and let "0s=suspect Blood Donor" to be "donor"
#cleanDF$Category <- cleanDF$Category %>% factor - this is original code, i change it to the following to make hepatitis as positive class.
cleanDF$Category <-factor(cleanDF$Category) %>% relevel("hepatitis") 
head(cleanDF, 10)
levels(cleanDF$Category)
head(cleanDF, 10)
summary(cleanDF[c("ALB","BIL","GGT")])

data_norm <- function(x) {((x - min(x)) / (max(x) - min(x)))}

testSet1 <- c(1:5)
testSet2 <- c(1:5)*10
cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")

#cat("Normalized testSet1:", normalize(testSet1), "\n") - this is orginal code that contain an error, normalize should be replace with the function name "data_norm" in this case
cat("Normalized testSet1:", data_norm(testSet1), "\n") 
#cat("Normalized testSet2:", normalize(testSet2)　) - this is orginal code that contain an error, normalize should be replace with the function name "data_norm" in this case
cat("Normalized testSet2:", data_norm(testSet2)　) 

summary(cleanDF)
cleanDF <- cleanDF %>% na.omit
cleanDF <- cleanDF[,-3] #this code is missing to remove unnumeric variables, so the function can run

nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(2:nCols,
                    function(x) {
                      data_norm(cleanDF[,x])
                    }) %>% as.data.frame() # I have replaced the function name "normalize" with "data_norm"

summary(cleanDF_n[c("ALB", "BIL", "GGT")])

trainDF_feat <- cleanDF_n[1:450,]
testDF_feat <- cleanDF_n[451:589,]

#trainDF_labels <- cleanDF[1:450, ] - this original code missing a 1 after the command to exclude the labels from the set
trainDF_labels <- cleanDF[1:450, 1]
#testDF_labels <- cleanDF[451:589, ] - this original code missing a 1 after the command to exclude the labels from the set
testDF_labels <- cleanDF[451:589, 1]
```


## Modeling
text and code here
```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), 
                         cl = as.matrix(trainDF_labels), k = 23)
head(cleanDF_test_pred) #k should be odd number, so I change it from 24 to 23

confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```


## Evaluation and Deployment

As a reviewer for Thanh's work, I have found and corrected a few errors to make it run smoothly. I have given explanations of the correction in the above by making notes on the code itself.
Apart from the errors, I also ran the model and saw that this model only have an accuracy of 0.59, which quite low to have for a model. As the accuracy of the model is depended on the quality of data set, I can assume that this data set and/or model is not efficient. Therefore, I think the overall performance of this model is not really acceptable as it is not very helpful with using it to classify the blood donors vs. Hepatitis C.